A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-26 4_method.tex
new VQ images

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
\caption{MAT}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
\caption{Limited VD}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
\caption{VQ}
\end{subfigure}
\caption{
Relation between the medial axis, the limited Voronoi Diagram and the Voronoi quadrangulation: MAT $\subset$ Limited VD $\subset$ VQ.
Significant parts of the skeleton are visualized in shades of red, insignificant regions in grey and blue.
}
\label{skeletonization_comparison}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/parabola_dip.pdf}
\caption{
Construction of a VQ:
the MAT in red,
the bones added by VD in purple,
the bones added by VQ in orange,
the bones added by discretization in dashed lines.
The 3 types of quad are highlighted.
}
\label{discretization}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Voronoi Quadrangulation (red, green and gray): MAT $\subset$ Limited VD $\subset$ VQ.
}
\label{skeletonization_comparison}
\end{figure}

@@

\begin{figure}
\centering
%\begin{subfigure}{0.45\textwidth}
%\includegraphics[width=\columnwidth]{sources/method/parabola_dip.pdf}
%\caption{asf}
%\end{subfigure}
%\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
%\caption{Transitioning}
%\end{subfigure}
\caption{
Voronoi quadrangulation domain decomposition.
Medial axis (red and blue) is augmented with (gray) edges connecting each node to its nearest support points in the outline shape.
Parabolic medial axis segments are discretized and likewise for segments generated by two concave outline vertices, because the feature radius (black text in microns) doesn't increase linearly along those segments.
The blue segments are significant according to $\alpha_\text{max} = 135\degree$.
}
\label{discretization}
\end{figure}
